---
title: "Lab 2, CP 4: Análise completa"
output: html_notebook
---

```{r setup}
library(tidyverse)
library(here)
library(lubridate)
theme_set(theme_bw())
```

```{r ETL}
buscas = read_csv(here::here("data/search_data.csv"))
```


## Manipulando os dados primeiro
```{r}

buscas %>% 
    group_by(group) %>% 
    summarise(n = n()) %>% 
    ggplot(aes(x = group, y = n, fill = group, color = group)) +
    theme(legend.position="none") +
    geom_col()

buscas %>% 
    mutate(date = floor_date(session_start_date, unit = "day")) %>% 
    count(date, group) %>%
    ggplot(aes(x = date, y = n, fill = "red")) +
    xlab("Data") +
    ylab("Contagem") +
    theme(legend.position="none") +
    geom_col()

buscas %>% 
    ggplot(aes(x = "Total de resultados", y = results)) + 
    geom_boxplot(outlier.shape=NA) +
    scale_y_log10()

buscas %>% 
    ggplot(aes(x = "Posição da página", y = click_position)) + 
    geom_boxplot(outlier.shape=NA) +
    scale_y_log10()

buscas %>% 
    ggplot(aes(x = "Resultados", y = results)) + 
    geom_boxplot(outlier.shape=NA) +
    scale_y_log10()
```

# Pergunta 1
### What is our daily overall clickthrough rate? How does it vary between the groups?
```{r}
buscas %>%
    mutate(date = floor_date(session_start_date, unit = "day")) %>% 
    count(date) %>%
    ggplot(aes(x = date, y = n)) +
    xlab("Data") +
    ylab("Contagem") +
    geom_line()+ 
    geom_point()

buscas %>%
    mutate(date = floor_date(session_start_date, unit = "day")) %>% 
    count(date, group) %>%
    ggplot(aes(x = date, y = n, fill = group, color = group)) +
    xlab("Data") +
    ylab("Contagem") +
    geom_line()+ 
    geom_point()

min(buscas$session_start_date)
max(buscas$session_start_date)
```
# Pergunta 2
### Which results do people tend to try first?
```{r}
summary(buscas$click_position)

buscas %>% 
    ggplot(aes(x = click_position)) + 
    scale_x_log10() +
    stat_ecdf()

statmod <- function(x) { 
z <- table(as.vector(x)) 
names(z)[z == max(z)] 
} 

statmod(buscas$click_position)
```

### How does it change day-to-day?

```{r}
buscas %>%
    mutate(date = floor_date(session_start_date, unit = "day")) %>%
    mutate(moda = statmod(click_position)) %>%
    count(date, moda) %>%
    ggplot(aes(x = date, y = moda)) +
    xlab("Data") +
    ylab("Moda") +
    geom_line() + 
    geom_point()
```


#Pergunta 3
### What is our daily overall zero results rate? How does it vary between the groups?

```{r}
buscas %>% # a taxa de resultados = 0 em cima dos resultados = 0 
    filter(buscas$results == 0) %>%
    mutate(date = floor_date(session_start_date, unit = "day")) %>% 
    ggplot(aes(date, fill="red")) +
    geom_bar(aes(y = (..count..)/sum(..count..))) +
    geom_text(aes( label = scales::percent(..prop..),y= ..prop.. ), stat= "count", vjust = -.3) +
    scale_y_continuous(labels=scales::percent) +
    theme(legend.position="none") +
    ylab("relative frequencies")

buscas %>% 
    filter(buscas$results == 0) %>%
    mutate(date = floor_date(session_start_date, unit = "day")) %>% 
    ggplot(aes(date, fill=group, group = group, color=group)) +
    geom_bar(aes(y = (..count..)/sum(..count..))) +
    scale_y_continuous(labels=scales::percent) +
    facet_grid(~group) +
    theme(legend.position="none") +
    ylab("relative frequencies")


buscas %>%
    filter(buscas$results == 0) %>%
    mutate(date = floor_date(session_start_date, unit = "day")) %>% 
    ggplot(aes(date, fill="red")) +
    geom_bar(aes(y = (..count..)/sum(..count..))) +
    geom_text(aes( label = scales::percent(..prop..), y= ..prop.. ), stat= "count", vjust = -.3) +
    scale_y_continuous(labels=scales::percent) +
    theme(legend.position="none") +
    ylab("relative frequencies")


buscas %>%
    filter(buscas$results == 0) %>%
    mutate(date = floor_date(session_start_date, unit = "day")) %>% 
    count(date) %>% 
    mutate(perc = sprintf("%0.2f",(n / nrow(buscas)) * 100)) %>%
    ggplot(aes(x = date, y = perc, fill="red")) + 
    theme(legend.position="none") +
    geom_bar(stat = "identity") +
    geom_text(aes(label=perc), position=position_dodge(width=0.9), vjust=-0.25)

```


```{r}

buscas %>% 
    mutate(date = floor_date(session_start_date, unit = "day")) %>% 
    mutate(resultCount = ifelse(buscas$results > 0, "Um ou mais resultados", "Zero resultados")) %>%
    count(date, resultCount) %>%
    ggplot(aes(x = date, y = n, fill = resultCount)) +
    xlab("Data") +
    ylab("Contagem") +
    geom_col() +
    geom_text(aes(label=sprintf("%0.2f%%",(n/nrow(buscas)) * 100)), position=position_dodge(width=0.5), vjust=-0.25) 

buscas %>% 
    mutate(date = floor_date(session_start_date, unit = "day")) %>% 
    mutate(resultCount = ifelse(buscas$results > 0, "Um ou mais resultados", "Zero resultados")) %>%
    count(date, resultCount, group) %>%
    ggplot(aes(x = date, y = n, fill = resultCount)) +
    xlab("Data") +
    facet_grid(~group) +
    ylab("Contagem") +
    geom_col()+
    geom_text(aes(label=sprintf("%0.2f%%",(n/nrow(buscas)) * 100)), position=position_dodge(width=0.2), vjust=-0.25) 

```


#Pergunta 4
### Let session length be approximately the time between the first event and the last event in a session. Choose a variable from the dataset and describe its relationship to session length. Visualize the relationship.
```{r}

buscas %>% 
    mutate(lenght = buscas$session_finish_timestamp - buscas$session_start_timestamp) %>% 
    ggplot(aes(x = "Tempo", y = lenght)) + 
    geom_boxplot(outlier.shape=NA) +
    scale_y_log10()

buscas %>%
    mutate(lenght = buscas$session_finish_timestamp - buscas$session_start_timestamp) %>% 
    ggplot(aes(x = group, y = lenght, color = group)) + 
    scale_y_log10() +
    geom_jitter(alpha = .3)

summary(filter(mutate(buscas,lenght = buscas$session_finish_timestamp - buscas$session_start_timestamp), group== "a")$lenght)
summary(filter(mutate(buscas,lenght = buscas$session_finish_timestamp - buscas$session_start_timestamp), group== "b")$lenght)
```